Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-02-12 manuscript/climate_sensitivity_SI.Rmd
insert Fig. S3
Updated file names to match figures

\newpage
![Figure S1: Map of ForestGEO plot showing TWI and location of cored trees](tables_figures/figureS2_location_cored_trees.png){width=500px}

\newpage
![Figure S2: Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to each focal drought](tables_figures/drought_plot.jpg){width=600px}

>>>>

\newpage
![Figure S1: Map of ForestGEO plot showing TWI and location of cored trees](tables_figures/figureS1_location_cored_trees.png){width=500px}

\newpage
![Figure S2: Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to each focal drought](tables_figures/figureS2_drought_plot.jpg){width=600px}

\newpage
![Figure S3: Changes in height by canopy position](tables_figures/figureS3_height_plot_analysis.png){width=600px}
